---
title: "Batch Processing & Quota Management"
author: "tuber maintainers"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Batch Processing & Quota Management}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Understanding YouTube API quotas

YouTube now tracks ordinary Data API units, search calls, and video-upload calls
in separate default buckets. Google Cloud Console remains the source of truth;
the package counters only estimate requests made by the current R session.

### Quota Costs by Operation

Different operations have different quota costs:

| Operation | Default accounting | Example function |
|-----------|-----------|------------------|
| Ordinary list request | 1 Data API unit | `get_video_details()` |
| Search request | 1 Search Query call | `yt_search()` |
| Typical write or delete | 50 Data API units | `create_playlist()`, `delete_video()` |
| Caption list, download, insert, update | 50, 200, 400, 450 Data API units | Caption functions |
| Video upload | 1 Video Upload call | `upload_video()` |

Google's default allocations are 10,000 Data API units, 100 Search Query calls,
and 100 Video Upload calls per day. These defaults can change or be increased
for a project.

### Tracking Quota Usage

tuber provides built-in quota tracking:

```{r quota-tracking, eval=FALSE}
library(tuber)

# Check current quota usage
quota_status <- yt_get_quota_usage()
print(quota_status)

# View details
quota_status[, c("bucket", "quota_used", "quota_limit", "quota_remaining")]
quota_status$reset_time[1] # Midnight Pacific Time
```

### Setting Custom Quota Limits

If you've requested a quota increase from Google, update your limit:

```{r set-quota, eval=FALSE}
# Set a custom quota limit
yt_set_quota_limit(50000, bucket = "data")

# Configure a project-specific search-call allocation
yt_set_quota_limit(200, bucket = "search")

# Reset quota tracking (e.g., after midnight)
yt_reset_quota()
```

## Authentication Strategies

tuber supports two authentication methods, each with different use cases.

### API Key Authentication

Best for **read-only public data**:
- Searching videos
- Getting public video statistics
- Fetching channel information
- Reading public comments

```{r api-key, eval=FALSE}
# Set up API key (get one from Google Cloud Console)
yt_set_key("YOUR_API_KEY")

# Use API key for read operations
video_stats <- get_video_details(
  video_ids = "dQw4w9WgXcQ",
  auth = "key"
)

channel_stats <- get_channel_details(
  channel_ids = "UCuAXFkgsw1L7xaCfnd5JJOw",
  auth = "key"
)
```

### OAuth2 Authentication

Required for:
- Accessing private/unlisted content
- Writing data (creating playlists, uploading videos)
- Deleting resources
- Accessing user's own channel data

```{r oauth, eval=FALSE}
# Set up OAuth2 (opens browser for authentication)
yt_oauth("YOUR_CLIENT_ID", "YOUR_CLIENT_SECRET")

# Write operations require OAuth
create_playlist(
  title = "My New Playlist",
  description = "A collection of favorites",
  status = "private"
)

# Access your own channel's unlisted videos
list_my_videos()
```

### Which Authentication to Use?

| Task | API Key | OAuth2 |
|------|---------|--------|
| Search public videos | Yes | Yes |
| Get public video stats | Yes | Yes |
| Get public channel info | Yes | Yes |
| Read public comments | Yes | Yes |
| Access unlisted videos (own) | No | Yes |
| Access private videos (own) | No | Yes |
| Create/update playlists | No | Yes |
| Upload videos | No | Yes |
| Delete content | No | Yes |
| Manage comments | No | Yes |

## Batch Processing

When working with many videos or channels, batch processing is essential for efficiency.

### Processing Multiple Videos

```{r batch-videos, eval=FALSE}
# Get details for multiple videos at once
video_ids <- c("dQw4w9WgXcQ", "M7FIvfx5J10", "kJQP7kiw5Fk")

# Single API call for multiple videos (more efficient)
videos <- get_video_details(
  video_ids = video_ids,
  part = c("snippet", "statistics"),
  auth = "key"
)

# Analyze results
head(videos)
```

### Using Bulk Analysis Functions

tuber provides high-level functions for common analysis tasks:

```{r bulk-analysis, eval=FALSE}
# Comprehensive video analysis
analysis <- bulk_video_analysis(
  video_ids = video_ids,
  include_comments = FALSE,
  auth = "key"
)

# Access results
analysis$video_data # Detailed video information
analysis$benchmarks # Performance percentiles
analysis$summary # Overall statistics

# Channel analysis
channel_analysis <- analyze_channel(
  channel_id = "UCuAXFkgsw1L7xaCfnd5JJOw",
  max_videos = 50,
  auth = "key"
)

# Compare multiple channels
comparison <- compare_channels(
  channel_ids = c("UC1", "UC2", "UC3"),
  metrics = c("subscriber_count", "video_count", "view_count"),
  auth = "key"
)
```

### Pagination Handling

tuber automatically handles pagination for large result sets:

```{r pagination, eval=FALSE}
# Request more items than API allows per page (50)
# tuber automatically makes multiple API calls
playlist_items <- list_playlist_items(
  playlist_id = "PLrAXtmErZgOeiKm4sgNOknGvNjby9efdf",
  max_results = 200, # Will make 4 API calls
  auth = "key"
)

# Get many comments with automatic pagination
comments <- list_comment_threads(
  video_id = "dQw4w9WgXcQ",
  max_results = 500, # Will paginate automatically
  auth = "key"
)
```

## Extracting Data from Results

YouTube API responses contain nested JSON. Here's how to work with them.

### Using simplify = TRUE (Default)

Most functions flatten nested data into data frames:

```{r extract-simple, eval=FALSE}
# Get simplified output
videos <- get_video_details(
  video_ids = "dQw4w9WgXcQ",
  simplify = TRUE,
  auth = "key"
)

# Access fields directly
videos$title
videos$viewCount
videos$likeCount
videos$channelTitle
```

### Using simplify = FALSE for Complex Data

When you need the full nested structure:

```{r extract-raw, eval=FALSE}
# Get raw API response
videos_raw <- get_video_details(
  video_ids = "dQw4w9WgXcQ",
  simplify = FALSE,
  auth = "key"
)

# Navigate nested structure
video <- videos_raw$items[[1]]
video$snippet$title
video$snippet$thumbnails$high$url
video$statistics$viewCount
video$contentDetails$duration
```

### Common Field Access Patterns

```{r field-patterns, eval=FALSE}
# Video details
videos$snippet.title # Title
videos$snippet.description # Description
videos$statistics.viewCount # View count
videos$statistics.likeCount # Like count
videos$contentDetails.duration # Duration (ISO 8601)

# Channel details
channels$snippet.title # Channel name
channels$statistics.subscriberCount
channels$statistics.videoCount
channels$brandingSettings.channel.description

# Comment extraction
comments$text_display
comments$author_name
comments$like_count
```

## Error Handling & Retries

### Using with_retry for Transient Errors

```{r retry, eval=FALSE}
# Automatic retry with exponential backoff
result <- with_retry(
  get_video_details(video_ids = "dQw4w9WgXcQ", auth = "key"),
  max_retries = 3,
  base_delay = 1
)
```

### Handling Quota Exhaustion

```{r quota-handling, eval=FALSE}
# Check before making data API requests
quota <- yt_get_quota_usage()
data_quota <- quota[quota$bucket == "data", ]
if (data_quota$quota_remaining < 100) {
  warning("Low quota! Consider waiting until reset at: ", data_quota$reset_time)
}

# Wrap expensive operations
tryCatch(
  {
    results <- yt_search(term = "R programming", max_results = 50)
  },
  error = function(e) {
    if (grepl("quota", e$message, ignore.case = TRUE)) {
      message("Quota exceeded. Try again after: ", yt_get_quota_usage()$reset_time)
    }
  }
)
```

### Rate Limiting Best Practices

```{r rate-limiting, eval=FALSE}
# Add delays between requests
video_ids <- c("id1", "id2", "id3", "id4", "id5")

results <- lapply(video_ids, function(vid) {
  Sys.sleep(0.5) # 500ms delay between requests
  get_video_details(video_ids = vid, auth = "key")
})
```

## Caching for Performance

tuber includes built-in caching for frequently accessed data:

```{r caching, eval=FALSE}
# Configure cache
tuber_cache_config(
  enabled = TRUE,
  max_size = 100,
  default_ttl = 3600
)

# Eligible GET requests are cached transparently
cats <- list_video_categories(region_code = "US", auth = "key")
langs <- list_languages(auth = "key")
regions <- list_regions(auth = "key")

# Check cache status
tuber_cache_info()

# Clear cache when needed
tuber_cache_clear()
```

## Practical Examples

### Example 1: Analyze a Channel's Performance

```{r example-channel, eval=FALSE}
# Full channel analysis
analysis <- analyze_channel(
  channel_id = "UCuAXFkgsw1L7xaCfnd5JJOw",
  max_videos = 100,
  auth = "key"
)

# Summary statistics
cat("Channel:", analysis$channel_info$title, "\n")
cat("Subscribers:", analysis$channel_info$subscriberCount, "\n")
cat("Average views:", analysis$performance_metrics$avg_views_per_video, "\n")
cat("Engagement rate:", analysis$performance_metrics$engagement_rate, "\n")
```

### Example 2: Trending Analysis

```{r example-trending, eval=FALSE}
# Analyze trending topics
trends <- analyze_trends(
  search_terms = c("machine learning", "AI", "data science"),
  time_period = "month",
  max_results = 25,
  region_code = "US",
  auth = "key"
)

# View trend summary
print(trends$trend_summary)

# Most trending term
best_trend <- trends$trend_summary[1, ]
cat("Top trending:", best_trend$search_term, "\n")
cat("Total views:", best_trend$total_views, "\n")
```

### Example 3: Efficient Video Processing

```{r example-batch, eval=FALSE}
# Get all videos from a playlist
playlist_videos <- list_playlist_items(
  playlist_id = "PLrAXtmErZgOeiKm4sgNOknGvNjby9efdf",
  max_results = 100,
  auth = "key"
)

# Extract video IDs
video_ids <- playlist_videos$video_id

# Get detailed stats for all videos in one call
video_stats <- get_video_details(
  video_ids = video_ids,
  part = c("statistics", "contentDetails"),
  auth = "key"
)

# Analyze performance
total_views <- sum(as.numeric(video_stats$viewCount), na.rm = TRUE)
avg_duration <- mean(as.numeric(video_stats$duration), na.rm = TRUE)
```

## Troubleshooting

### Common Issues

**"quotaExceeded" error:**
- Check quota with `yt_get_quota_usage()`
- Wait until `reset_time` or request quota increase from Google

**"forbidden" error:**
- Ensure YouTube Data API is enabled in Google Cloud Console
- Check API key/OAuth credentials are correct
- Verify the resource isn't private

**"videoNotFound" or empty results:**
- Video may be private, deleted, or region-restricted
- Double-check the video/channel ID format

**Rate limiting (429 errors):**
- Add delays with `Sys.sleep()` between requests
- Use `with_retry()` for automatic backoff

### Getting Help

```{r help, eval=FALSE}
# Check function documentation
?get_video_details
?yt_search
?with_retry

# View package vignettes
browseVignettes("tuber")
```
