### tuber: Access YouTube via R

#### Load the package

To get started, load the package. The latest version of the package will always be on github. Instructions for installing the package from github are provided below.



```r
library(tuber)
```


```r
"
Get the latest version from github:

# install.packages('devtools')
devtools::install_github('soodoku/tuber')
"
```

To get going, get the application id and password from [https://cloud.google.com/console](https://cloud.google.com/console). Enable YouTube APIs. Then set the application id and password via the `yt_oauth` function. For more information about YouTube OAuth, see [YouTube OAuth Guide](https://developers.google.com/youtube/v3/guides/authentication).

```{r yt_oauth}
yt_oauth("app_id", "app_password")
```

**Get Statistics of a Video**

```{r get_stats}
get_stats(video_id="N708P-A45D0")
```

**Get Information About a Video**

```{r get_stats}
get_details(video_id="N708P-A45D0")
```

**Get Caption of a Video**

```{r get_captions}
get_captions(video_id="yJXTXN4xrI8")
```

**Search Videos**
```{r yt_search}
yt_search("Barack Obama")
```

